\section{Discussion}
\label{sec:discuss}

Figure~\ref{plot-hinton} is the Hinton diagram of Penn Treebank WSJ
showing the relationship between the most frequent tags and clusters
from the experiment in Section~\ref{sec:feat}.  In general the errors
seem to be the lack of completeness (multiple large entries in a row),
rather than lack of homogeneity (multiple large entries in a column).
The algorithm tends to split large word classes into several clusters.
Some examples are:
\begin{itemize}
\item Titles like Mr., Mrs., and Dr. are split from the rest of the
  proper nouns in cluster (39).
\item Auxiliary verbs (10) and the verb ``say'' (22) have been split
  from the general verb clusters (12) and (7).
\item Determiners ``the'' (40), ``a'' (15), and capitalized
  ``The'', ``A'' (6) have been split into their own clusters.
\item Prepositions ``of'' (19), and ``by'', ``at'' (17) have been
  split from the general preposition cluster (8).
\end{itemize}
Nevertheless there are some homogeneity errors as well:
\begin{itemize} 
\item The adjective cluster (5) also has some noun members probably
  due to the difficulty of separating noun-noun compounds from
  adjective modification.
\item Cluster (6) contains capitalized words that span a number of
  categories.
\end{itemize}
%% A comparison of morphological structures might be helpful.
%% 
Most closed-class items are cleanly separated into their own clusters
as seen in the lower right hand corner of the diagram. 

The completeness errors become more noticable on languages with coarse
tagset thus our models perform worse than the best published models on
6 of MULTEXT-East languages in terms of \vm scores while achieving the
state-of-the-art \mto scores on same languages as shown on
Table~\ref{multiresults}.  On CONLL-X languages the effect of
completeness errors is less noticable since all languages except Czech
and Dutch have fine grained tagsets.

As the tagset of languages becomes fine grained the effect of
completeness errors decreases as it is the case

The completeness errors are not surprising given that the words that
have been split are not generally substitutable with the other members
of their gold-tag set category.  Thus it can be argued that metrics
that emphasize homogeneity such as \mto are more appropriate in this
context than metrics that average homogeneity and completeness such as
\vm as long as the number of clusters is controlled.

